Generating a README.txt file for the Dryad submission of data from study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-18 dryad/README.Rmd
adding newick files of cross validated chronograms to dryad folder

# get only newick file names
newick_files <- files_in_path[grep("[.]tre", files_in_path)]

@@

index <- 1
for (file_name in newick_files) {
  index <- index + 1
  file.copy(from = paste0("../figures/figure-fringillidae/source_chronograms/", file_name),
          to = paste0("../dryad/Sanchez-Reyes_etal_2022_supplementary_figure_S", index, "_source.tre"),
          overwrite = TRUE)
}
```

>>>>

# get source chronograms newick file names
newick_files <- files_in_path[grep("[.]tre", files_in_path)]

@@

index <- 1
for (file_name in newick_files) {
  index <- index + 1
  file.copy(from = paste0("../figures/figure-fringillidae/source_chronograms/", file_name),
          to = paste0("../dryad/Sanchez-Reyes_etal_2022_supplementary_figure_S", index, "_source.tre"),
          overwrite = TRUE)
  write(paste0("https://raw.githubusercontent.com/LunaSare/datelifeMS1/main/dryad/Sanchez-Reyes_etal_2022_supplementary_figure_S", index, "_source.tre"), file = "../dryad/urls.txt", append=TRUE)
}

# get cross validated chronograms newick file names
files_in_path <- list.files(path = "../figures/fringillidae-cross-validation")

newick_files <- files_in_path[grep("[.]tre", files_in_path)]

index <- 1
for (file_name in newick_files) {
  index <- index + 1
  file.copy(from = paste0("../figures/fringillidae-cross-validation/", file_name),
          to = paste0("../dryad/Sanchez-Reyes_etal_2022_supplementary_figure_S", index, "_cross_validated.tre"),
          overwrite = TRUE)
  write(paste0("https://raw.githubusercontent.com/LunaSare/datelifeMS1/main/dryad/Sanchez-Reyes_etal_2022_supplementary_figure_S", index, "_cross_validated.tre"), file = "../dryad/urls.txt", append=TRUE)
}
